`make.events`

### 2021-01-19 inst/gitbook/04_make.events.Rmd
Added 3D example

@@

## Event changing a trait correlation
change_correlation <- make.events(
    condition    = trait.condition(3, absolute = TRUE),
    target       = "traits",
    modification = update.traits(process.args = list(Sigma = matrix(c(10,3,3,2),2,2))))

## Run the simulations
set.seed(8)
no_event <- dads(bd.params = bd.params,
                 stop.rule = stop.rule,
                 traits    = traits)
set.seed(8)
change_correlation <- dads(bd.params = bd.params,
                           stop.rule = stop.rule,
                           traits    = traits,
                           events    = change_correlation)
## Visual testing
par(mfrow = c(1,2))
plot(no_event, trait = 2)
plot(change_correlation, trait = 2)
# plot(no_event, trait = c(1:2))
# plot(change_correlation, trait = c(1:2), use.3D = TRUE)
```

@@

## Visualise the results
par(mfrow = c(1,2))
plot(no_event, main = "No event")
plot(change_spec, main = "Increase extinction for negative traits\nafter time 3")
```

>>>>

```{r, echo = FALSE}
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```

@@

## Event changing a trait correlation
cor_change <- make.events(
    condition    = trait.condition(3, absolute = TRUE),
    target       = "traits",
    modification = update.traits(process.args = list(Sigma = matrix(c(10,3,3,2),2,2))))

## Run the simulations
set.seed(2)
no_event <- dads(bd.params = bd.params,
                 stop.rule = stop.rule,
                 traits    = traits)
set.seed(2)
change_correlation <- dads(bd.params = bd.params,
                           stop.rule = stop.rule,
                           traits    = traits,
                           events    = cor_change)

## Visual testing
par(mfrow = c(1,2))
plot(no_event, trait = 2)
plot(change_correlation, trait = 2)

```

```{r, webgl=TRUE}
## 3D plot
plot(change_correlation, trait = c(1:2), use.3D = TRUE)
```

@@

## Visualise the results
par(mfrow = c(1,2))
plot(no_event, main = "No event")
plot(change_spec, main = "Increase extinction for negative\ntraits after time 3")
```
